Audio Transport

### 2017-05-14 Paper/paper.tex
Added phase unwrapping, didn't really work. What if I just linearly interpolated the spectras once they've moved?? They couldn't interfere if they're centered to the same space

@@

\subsection{STFT}
Weighted overlap add
root hann window
Let $M$ be the window size, $R$ be the hopsize.

We are guaranteed perfect reconstruction in the absense of spectral modifications if
\begin{align*}
  \sum_m w^2(n - mR) = 1,\;\forall n\in\mathbb{Z}
\end{align*}
I choose the to use the root Hann window.
\begin{align*}
  w(n) = 
  \cos(\pi n / M), 
  n\in
  \left[
  -\frac{M-1}{2}, 
  \frac{M-1}{2}
\right]
\end{align*}

\subsection{Spectrum Segmentation}
In order to fix the spec
Techniques mention peak finding.
However peak finding does not give a great sense of where to put boundaries. 
The reassigned frequency can be computed by:
\begin{align}
  \hat{\omega}(\omega) = 
  \omega + 
  \Im\left\{%
    \frac{X_\mathcal{D}(\omega)\cdot X^*(\omega)}{|X(\omega)|^2}
  \right\}
\end{align}
where $X_\mathcal{D}$ is the spectrum of the $x$ with the window
$w_\mathcal{D}(n) = \frac{d}{dt}w(n)$:
\begin{align}
  X_\mathcal{D}(\omega) = \fft\left(w_\mathcal{D}(n)x(n)\right)
\end{align}
d(root hann window)
\begin{align*}
   w_\mathcal{D}(n) = -\frac{\pi f_s}{M}\sin\left(\frac{\pi n}{M}\right)
\end{align*}

@@

\section{Implementation}
Real time.
\texttt{fftw}

>>>>

\section{Contributions}

I developed an algorithm that

techniques to
reconstruct an audio signal

I use a new technique to segment the spectrum into smaller pieces.
Phase reconstruction

I also implemented the algorithm in real-time to

@@

\subsection{STFT}

Like almost all spectral algorithms, this one begins with a short-time Fourier transform (STFT) and ends with it's inverse (ISTFT).
At the cost of reduced temporal resolution, the STFT gives us access to the spectral contents of the signal in time.

The STFT fourier transform performs a discrete time Fourier transforms on windows of size $M$ of the original signal $x(n)$. 
These windows are separated by a hop size of $R$. The $m$th frame of the STFT is

\begin{align}
  X_m(\omega) = 
  \sum_{n = -\frac{M-1}{2}}^{\frac{M - 1}{2}} 
  x_m(n)w(n)e^{-i\omega n}
\end{align}

$x_m(n) = x(n + mR)$ 
is a buffer of size $M$ of the original signal
shifted $R$ samples from the previous buffer.
$w(n)$ is the synthesis window of size $M$.

The ISTFT can then reconstruct the
original signal by

In the absence of spectral modifications, 
we can achieve perfect reconstruction 
of a signal given that the synthesis and analysis windows obey
\begin{align}
  \sum_m w(n - mR)f(n - mR) = 1,\; \forall n\in \mathbb{Z}
\end{align}

I chose to use the root Hann window, which gives perfect reconstruction when $R = \frac{M}{2k}$ for $k\in\mathbb{Z}$.
\begin{align*}
  w(n) = 
  \cos(\pi n / M), 
  n\in
  \left[
  -\frac{M-1}{2}, 
  \frac{M-1}{2}
\right]
\end{align*}

\subsection{Spectrum Segmentation}

In order to resolve the vertical incoherence --- the phasing issues within the frame --- my solution like others is to lock regions of the spectrum where phase relations are important. Rather than performing a transport over all bins, bins which are used to represent the same spectral information are lumped together.

TODO
Many applications use simple peak finding, which is good in most appliccations but fails in certain settings.
Instead I determine where to split the window based on the \emph{reassigned frequency}.
The reas

In order to fix the spec
Techniques mention peak finding.
However peak finding does not give a great sense of where to put boundaries. 
The reassigned frequency can be computed by:
\begin{align}
  \hat{\omega}(\omega) = 
  \omega + 
  \Im\left\{%
    \frac{X_\mathcal{D}(\omega)\cdot X^*(\omega)}{|X(\omega)|^2}
  \right\}
\end{align}
where $X_\mathcal{D}$ is the spectrum of the $x$ with the window
$w_\mathcal{D}(n) = \frac{d}{dt}w(n)$:
\begin{align}
  X_\mathcal{D}(\omega) = \fft\left(w_\mathcal{D}(n)x(n)\right)
\end{align}
d(root hann window)
\begin{align*}
   w_\mathcal{D}(n) = -\frac{\pi f_s}{M}\sin\left(\frac{\pi n}{M}\right)
\end{align*}

@@

\section{Implementation}

I implemented the above algorithm in real-time as an audio effect in C++.
The program listens to two streams of audio
which can be sent to it from a any diginal audio workstation, like Ableton Live.
It then produces a new stream of audio that is interpolated between the two original streams according to a MIDI value.

Real time.
\texttt{fftw}
